---
output: html_document
editor_options: 
  chunk_output_type: console
---
All the packages I need and some plot options.

```{r}
setwd("/home/suhishan/Documents/Final Sem Research/Conflict/")
library(haven)
library(tidyverse)
library(stargazer)
library(patchwork)
library(dagitty)
library(sf)
library(ddecompose)

theme_set(theme_minimal() +
            theme(panel.grid = element_blank()))

```


#Load Datasets.

```{r}
nlfs <- read_dta("appended_nlfs.dta") # Only people aged 10 and above. 
c <- read_dta("final_conflict.dta")

# Renaming and mutating most of the variables that I will need.


#select only the relevant variables. 
c <- c %>% select(
  distname, elevation_max,norm_forest, pov_rate, district_abbrev, best_est, 30:51, incidents
)

c <- c %>% mutate(
    forest_cover = round(norm_forest*100, 2),
    poverty_rate = round(pov_rate* 100, 2), #note: Dolpa, Mustang and Rasuwa don't have poverty rate estimates.
    # manang and mustang (NA no conflict deaths) turned to 0 
    conflict_deaths = ifelse(is.na(best_est),
                             0,
                             best_est)
    )

```

# Figuring out Temporary Treatment and Control. 

This is temporary for now: I'll probably use districts with extremely high conflict deaths as treatment and rest as control. 

```{r}

# histogram of deaths. 
c %>% 
  ggplot(aes(x = conflict_deaths)) +
  geom_histogram(color = "black", fill = "firebrick", bins = 30)

#t-plot of deaths. 

c %>% 
  ggplot(aes(x = 1:length(conflict_deaths), y = conflict_deaths))+
  geom_point(shape = 1, color = "firebrick")

# For now, let's divide the data into two parts, conflict deaths > 75th percentile  as treatment and others  as control. Just for testing everything. 

c <- c %>% mutate(
  treatment_crude = 
    ifelse(conflict_deaths > quantile(conflict_deaths, 0.75), 
                           1, 0)
)

# Let's see different histograms for crude treatment and how many are on the boundary. 

c %>% 
  ggplot(aes(x = 1:length(conflict_deaths), y = deaths_96 + deaths_97 + deaths_98))+
  geom_point(aes(color = treatment_crude), size = 3)
  
# For now the division is really crude, but we can use all kinds of divisions. # This is just for now really. and also it is crude. 

  
```


#Controlling for stuff using 1998 (pre-treatment variables)

Let's merge with the nlfs data:

```{r}
c_merged <- left_join(nlfs, c, by = c("district_abbrev"))

c_merged <- c_merged %>% mutate(
  id = as.numeric(1:n()),
  post = as.double(ifelse(nlfs_year == 2008, 1, 0)),
  treatment_crude = as.double(treatment_crude),
  brahmin_chhetri = as.double(brahmin_chhetri),
  hindu = as.double(hindu),
  usually_emp = as.factor(usually_emp),
  age = as.double(age),
  years_of_edu = as.double(years_of_edu)
)



```

I want to calculate normalized difference table like that in DiD practitioner's guide Page 16.x

What are the variables that I should look at observable differences of:

Thinking out loud: Age, years of education, being a Hindu, being a Brahmin/Chetri, being a woman, these are all correlated with whether you are usually employed or not. If these relationships would've held in the absence of Maoist conflict, and if more conflict and less conflict districts, differ in these demographic and economic characteristics, then parallel trends assumption may fail to hold. 

Let's now look at baseline (1998, t = 1) covariate levels between high-conflict and low-conflict districts. 

```{r}
#function to calculate normalized difference
norm_difference <- function(t, x) {
  mean_t <-  mean(x[t == 1], na.rm = T)
  mean_c <-  mean(x[t == 0], na.rm = T)
  sd_t <-  sd(x[t == 1],na.rm =T)
  sd_c <- sd(x[t==0], na.rm = T )
  norm_diff = (mean_t - mean_c) / sqrt(0.5 * (sd_t^2 * sd_c^2))
  return (round(norm_diff, digits = 4))
}

c_merged_98 <- c_merged %>% filter(nlfs_year == 1998)


c_merged_98 %>% 
  select(age, years_of_edu_all, years_of_edu, hindu,
         brahmin_chhetri, sex, marital_status,
         treatment_crude, hhsize,
         ever_school) %>% 
  summarize(across(
    .cols = -treatment_crude,
    .fns = list(
      norm_diff = ~norm_difference(treatment_crude, .x),
      mean_t  = ~ mean(.x[treatment_crude == 1], na.rm = T),
      mean_c = ~mean(.x[treatment_crude == 0], na.rm = T)),
    .names = "{fn}_{.col}"
  )) %>% 
 pivot_longer(
    cols = everything(),
    names_to = "stat_var", values_to = "value"
  ) %>% 
  extract(stat_var, into = c("stat", "variable"),
          regex = "(norm_diff|mean_t|mean_c)_(.+)") %>% 
  pivot_wider(
    names_from = stat, values_from = value
  )



```




