---
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
setwd("/home/suhishan/Documents/Final Sem Research/Conflict/")
library(haven)
library(tidyverse)
library(stargazer)
library(geodata)
library(sf)
library(patchwork)

theme_set(theme_minimal() +
            theme(panel.grid = element_blank()))

options(scipen = 999)
```

On classification into treatment and control:
There are a lot of misspecification tests that one must conduct but I will do that later. 

```{r}
c <- read_dta("Conflict Data/conflict_collapsed.dta")

c <- c  %>% 
  mutate(forest_cover = round(norm_forest * 100, 3),
         poverty_rate = round(pov_rate * 100, 3),
         high_forest = ifelse(forest_cover > quantile(forest_cover, 0.75, na.rm =T),1, 0))

```

First Stage Plot of Forest Cover and Conflict Deaths.

```{r}

q_75 <-  quantile(c$forest_cover, 0.75, na.rm = T)
firststage_plot <- c %>% 
  ggplot(aes(x = forest_cover, y = best_est))+
  geom_point(color = "#C70039", size =2.5)+
  geom_smooth(method = "lm", se = T,
              color = "black",
              size = 0.5)+
  geom_vline(xintercept =q_75,
             linetype = 2)+
 geom_rect(aes(xmin = q_75, xmax = Inf, ymin = -Inf, ymax = Inf),
            fill = "#ffb6c1", alpha = 0.01, inherit.aes = FALSE) +
  annotate("text", x  = q_75,
           y = 550,
           label = "75th Percentile Forest Cover")+
  xlab("Forest Cover Percentage in 1994")+
  ylab("Total Conflict Deaths")+
  labs(
    title = "Forest Cover as instrument for Conflict Deaths",
    subtitle = "Conflict Deaths here is Total Conflict Deaths from 1996 to 2006"
  )
firststage_plot

ggsave("firststage.jpg", plot = firststage_plot, path = "Data Presentation",
       bg = "white", width = 15, height = 10, units = "cm")


```


Counting districts higher/lower than 75th percentile forest cover.

```{r}
c %>% 
  filter(forest_cover > quantile(forest_cover, 0.65, na.rm =T)) %>% 
  select(distname, incidents, best_est) %>% 
  ggplot(aes(x = best_est))+
  geom_histogram(bins = 30)+
  theme_minimal()


c %>% 
  filter(forest_cover <  quantile(forest_cover, 0.65, na.rm =T)) %>% 
  select(distname, incidents, best_est) %>% 
  ggplot(aes(x = best_est))+
  geom_histogram(bins = 30)+
  theme_minimal()

c %>% 
  mutate(index = 1:n(),
         treatment = ifelse(
           forest_cover > quantile(forest_cover, 0.75, na.rm = T), 
           1, 
           0
         ) ) %>% 
  ggplot(aes(x = index, y = incidents))+
  geom_point(aes(color = as.factor(treatment)))
  

```


Let's make a map with conflict deaths.

```{r}
# read district names and geospatial information from the shape file. 
districts <- st_read("Nepal Shapfiles GADM/gadm36_NPL_3.shp") 

districts <- districts %>% 
  mutate(NAME_3 = tolower(NAME_3)) #district names to lowercase for merging.

c <- c %>% filter(distname != "") %>% 
  mutate(distname = tolower(distname)) # using plain old distname and NOT district_abbrev to merge with geospatial districts

districts_joined <- left_join(
  districts, c, by = c("NAME_3" = "distname")
)

```

Constructing and Plotting Conflict Deaths
```{r}
p1 <- ggplot(districts_joined) +
  geom_sf(aes(fill = log1p(best_est)), color = "white", size = 0.2) +
  scale_fill_gradient(
    low = "#ffe6f6",
    high = "#990000",
    na.value = "grey90",
    name = "Deaths",
    breaks = log1p(c(0, 50, 100, 200, 400, 800)),
    labels = c(0, 50, 100, 200, 400, 800)
  ) +
  labs(
    title = "Total Conflict Deaths by District (Maoist Insurgency, Nepal)",
    subtitle = "Circa 1996-2006",
    caption = "Data source: Uppsala Conflict Data Program",
    fill = "Conflict Deaths"
  ) +
  theme_minimal()

ggsave("conflict_map.jpg", plot = p1, path = "Data Presentation", bg = "white",
       width = 15, height = 10, units = "cm")
```


Constructing and Plotting Forest Level.

```{r}
p2 <- ggplot(districts_joined) +
  geom_sf(aes(fill = forest_cover), color = "white", size = 0.2) +
  scale_fill_gradient(
    low = "#bcb88a",
    high = "#013220",
    na.value = "grey90",
    name = "Forest Cover (%)"
  ) +
  labs(
    title = "Percentage of District covered by Forest (1994)",
    caption = "Forest Resources of Nepal(1987-1998)",
    fill = "Forest Cover"
  ) +
  theme_minimal()
ggsave("forest_map.jpg", plot = p1, path = "Data Presentation", bg = "white",
       width = 15, height = 10, units = "cm")


p1 | p2

ggsave("double_map.jpg", plot = p1 / p2, path = "Data Presentation", bg = "white",
       width = 25, height = 20, units = "cm")

```


Plotting Treatment and Control Districts:

```{r}

districts_joined <- districts_joined %>% 
  mutate(treatment_65 = ifelse(
    forest_cover > quantile(forest_cover, 0.65, na.rm = T), 
           1, 
           0
  ))
  
p3 <- 
  ggplot(districts_joined) +
  geom_sf(aes(fill = factor(treatment_65)), color = "white", size = 0.2) +
  labs(
    title = "Treatment and Control Districts",
    subtitle = "Treatment Status determined by districts whose forest cover is higher than the 65th percentile",
    caption = "NLFS 1 (1998/99)",
    fill = "Treatment Status"
  )+
  geom_sf_text(
    data = subset(districts_joined, treatment_65 == 1),
    aes(label = district),
    size = 2,
    color = "white"
  ) +
  scale_fill_manual(
    values = c("1" = "#ff474c", "0" = "#0077b6"),
    labels = c("Treatment", "Control"),
    name = "Treatment Status"
  )
p3


p4 <- ggplot(districts_joined) +
  geom_sf(aes(fill = factor(treatment)), color = "black",
          size = 0.2, alpha = 0.8) +
  labs(
    title = "Treatment and Control Districts",
    subtitle = "Treatment Status determined by districts whose forest cover is higher than the 75th percentile",
    caption = "NLFS 1 (1998/99)",
    fill = "Treatment Status"
  )+
  geom_sf_text(
    data = subset(districts_joined, treatment == 1),
    aes(label = district),
    size = 2,
    color = "black"
  ) +n
  scale_fill_manual(
    values =c( "0" = "white", "1" = "#800000"),
    labels = c("Control", "Treatment"),
    name = "Treatment Status"
  )

ggsave("treatment.jpg", plot = p4, path = "Data Presentation", bg = "white",
       width = 30, height = 15, units = "cm")
(p1 | p4)
```

