---
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r}
setwd("/home/suhishan/Documents/Final Sem Research/Conflict/")
library(haven)
library(tidyverse)
library(stargazer)
library(geodata)
library(sf)
library(patchwork)

#These packages are for html scraping.
library(rvest)
library(xml2)

theme_set(theme_minimal() +
            theme(panel.grid = element_blank()))

options(scipen = 999)

```


#### Adding Population of each District from Census 1991

```{r}
c <- read_dta("Conflict Data/conflict_collapsed.dta")
c %>% View()

# Reading the html file.
censustable_1 <- read_html("CENSUSTABLE 1.htm")
tables <- censustable_1 %>% 
  html_element("table")


tables_df <- 
  tables %>% html_table(fill = T) 
  select(X1,X3) %>% 
  rename( name = X1, population = X3
  ) %>% 
  mutate(
    name = case_when(
      name == "DHANKUTA" ~ "dhak",
      name == "SINCHUPALCHOKE" ~ "sinp",
      name == "TERHATHUM" ~ "tehr",
      name == "DADELDHURA" ~ "dadh",
      name == "DOLKHA" ~ "DOLAKHA",
      TRUE ~ name
    )
  ) %>% 
  mutate( district_abbrev = tolower(substr(name, 1, 4)))

```



####   Merge the Population with the conflict collapsed data.

```{r}
c <- left_join(c, tables_df, by = "district_abbrev" )

c <- c %>% mutate(
  population = as.numeric(population),
  deaths_per_1000 = (best_est/population) * 1000
) 

c <- c  %>% 
  mutate(forest_cover = round(norm_forest * 100, 3),
         poverty_rate = round(pov_rate * 100, 3),
         
         high_forest = ifelse(forest_cover > quantile(forest_cover, 0.75, na.rm =T), 1, 0))

```


#### The above population data had no male and female so extracting data from a different source (CENSUSTABLE 3)

```{r}
censustable_3 <- read_html("2001 Census Tables/CENSUSTABLE 3.htm")
censustable_3 <- censustable_3 %>% html_element("table") %>% 
  html_table(fill = T)

popn_df <- censustable_3 %>% 
  select(X1:X3, X5) %>% 
  rename(
    Group = X1,
    TotalPopn = X2, 
    MalePopn = X3,
    FemalePopn = X5
  ) %>% 
  mutate(rownumber = 1:n()) %>% 
  filter(rownumber>4 & rownumber !=86)

View(popn_df)
```






#### Now let's extract the usually employed status from TABLE 61.

```{r}
emp_table <- read_html("2001 Census Tables/TABLE 61.htm")
emp_tables <- emp_table %>% 
  html_element("table") %>% 
  html_table(fill = T) %>% 
  mutate(row = row_number())

```

Let's filter out the needed information.

```{r}
#filtered out the needed rows
both_sexes_rows <- emp_tables %>% filter(
  X1 == "BOTH SEXES" | X1 == "MALE"
   | X1 == "FEMALE"
)


#Extracted district/location name which is always in row-2 of "BOTH SEXES"
# and merged them together using left join.

district_info <- both_sexes_rows %>% 
  mutate(district_row = row - 2) %>% 
  left_join(emp_tables, by = c("district_row" = "row")) %>% 
  select(X1.x, X2.x, X5.x, X6.x, X7.x, row, district_row, X1.y) %>% 
  rename(district_name = X1.y)


# Left join doesn't work for male and female because male/female are not in row-2 of both sexes. Instead some random info takes place. So turn that info to NA and then fill the remaining with district names. 

emp_info <- district_info %>% 
  arrange(row) %>% 
  mutate(
   district_name = ifelse(startsWith(district_name, "INDUSTRY"), NA, district_name)
  ) %>% 
  fill(district_name, .direction = "down") 

names(emp_info) <- c("Group", "TotEmp","six_seven_months","eight_more_months", "NotStated","row","district_row","district_name")

emp_info <- emp_info %>% 
  mutate(six_seven_months = as.numeric(six_seven_months), 
         eight_more_months = as.numeric(eight_more_months),
         morethan_six = six_seven_months + eight_more_months) %>% 
  select(Group, morethan_six, district_name) %>% 
  pivot_wider(
    names_from = Group,
    values_from = morethan_six
  ) %>%
  mutate(
    MALE = ifelse(district_name == "LAMJUNG", 30661, MALE),
    FEMALE = ifelse(district_name == "LAMJUNG", 38096, FEMALE)
  ) %>% 
  mutate(
    total_emp = as.numeric(`BOTH SEXES`),
    male_emp = as.numeric(MALE),
    female_emp = as.numeric(FEMALE)
  ) %>% 
  select(1, 5:7) %>% 
  add_row(district_name = "TANAHUN", total_emp = 107648, male_emp = 50941,
          female_emp = 56707) # there was some issue with tanahun data so bruteforcing entry.

View(emp_info)
```


Now let's extract the age info.

```{r}
age_table <- read_html("2001 Census Tables/TABLE4.2.htm")
age_table2 <- read_html("2001 Census Tables/TABLE4.1.htm")
age_table3 <- read_html("2001 Census Tables/TABLE 4.htm")
age_tables  <- age_table %>% 
  html_element("table") %>% 
  html_table(fill = T) %>% 
  mutate(row = row_number())

age_tables2 <- age_table2 %>% 
  html_element("table") %>% 
  html_table(fill = T) %>% 
  mutate(row = row_number())

age_tables3  <- age_table3 %>% 
  html_element("table") %>% 
  html_table(fill = T) %>% 
  mutate(row = row_number())


```
Let's now do the data wrangling.

```{r}
names(age_tables) <- c("AgeGroup", "Total", "TotalPct", "Male", "MalePct", "Female", "FemalePct", "Row","District")

age_tables <- age_tables %>% 
  mutate(TotalPct = as.numeric(TotalPct), #convert chr to numeric
         MalePct = as.numeric(MalePct),
         FemalePct = as.numeric(FemalePct),
         
         AgeGroup = str_replace_all(AgeGroup, "\\s+", " "), #any large spaces replaced by a space for regex later on.
         ) %>%
  mutate(
    AgeGroup = str_trim(AgeGroup), #trimming the front and back of string for regex later on
    District = ifelse(!is.na(TotalPct) & TotalPct == 100, AgeGroup, NA)
  ) %>% 
  fill(District, .direction = "down")

under10 <- age_tables %>% 
  filter(grepl("^UNDER 1 YR\\.$|^[1-9] YEAR(S)?$|^10 YEARS$", AgeGroup)) %>% #extracting under 10 years old
  mutate(TotalPct = parse_number(as.character(TotalPct)))

result_age <- under10 %>% 
  group_by(District) %>% 
  summarize( #calculating cumulative percentages
    cumUnder10 = sum(TotalPct, na.rm = T),
    cumUnder10M = sum(MalePct, na.rm = T),
    cumUnder10F = sum(FemalePct, na.rm = T)) %>% 
  mutate(
    cumUnder10 = ifelse(District == "MYAGDI", 30.9, cumUnder10), #Myagdi bruteforced data
    cumUnder10M = ifelse(District == "MYAGDI", 32.6, cumUnder10M),
    cumUnder10F = ifelse(District == "MYAGDI", 29.1, cumUnder10F)
  ) %>% 
  add_row(District = "DHANUSA", cumUnder10 = 34.3, cumUnder10M = 34.5,
          cumUnder10F = 34.1) %>% 
  add_row(District = "PARBAT", cumUnder10 = 32.4, cumUnder10M = 35.2,
          cumUnder10F = 30) 
  

print(result_age)
  
```

For the remaining districts:

```{r}
names(age_tables2) <- c("AgeGroup", "Total", "TotalPct", "Male", "MalePct", "Female", "FemalePct", "Row", "District")

age_tables2 <- age_tables2 %>% 
  mutate(TotalPct = as.numeric(TotalPct),
          MalePct = as.numeric(MalePct),
         FemalePct = as.numeric(FemalePct),
        
         AgeGroup = str_replace_all(AgeGroup, "\\s+", " "),
         ) %>%
  mutate(
    AgeGroup = str_trim(AgeGroup),
    District = ifelse(!is.na(TotalPct) & TotalPct == 100, AgeGroup, NA)
  ) %>% 
  fill(District, .direction = "down")

under10_2 <- age_tables2 %>% 
  filter(grepl("^UNDER 1 YR\\.$|^[1-9] YEAR(S)?$|^10 YEARS$", AgeGroup)) %>% 
  mutate(TotalPct = parse_number(as.character(TotalPct)))

result_age_2 <- under10_2 %>% 
    group_by(District) %>% 
  summarize(
    cumUnder10 = sum(TotalPct, na.rm = T),
    cumUnder10M = sum(MalePct, na.rm = T),
    cumUnder10F = sum(FemalePct, na.rm = T))


print(result_age_2)

```

For Eastern Development Region : The third table. 

```{r}
names(age_tables3) <- c("AgeGroup", "Total", "TotalPct", "Male", "MalePct", "Female", "FemalePct", "Row","District")

age_tables3 <- age_tables3 %>% 
  mutate(TotalPct = as.numeric(TotalPct),
          MalePct = as.numeric(MalePct),
         FemalePct = as.numeric(FemalePct),
        
         AgeGroup = str_replace_all(AgeGroup, "\\s+", " "),
         ) %>%
  mutate(
    AgeGroup = str_trim(AgeGroup),
    District = ifelse(!is.na(TotalPct) & TotalPct == 100, AgeGroup, NA)
  ) %>% 
  fill(District, .direction = "down")

View(age_tables3)

under10_3 <- age_tables3 %>% 
  filter(grepl("^UNDER 1 YR\\.$|^[1-9] YEAR(S)?$|^10 YEARS$", AgeGroup)) %>% 
  mutate(TotalPct = parse_number(as.character(TotalPct)))



result_age_3 <- under10_3 %>% 
    group_by(District) %>% 
  summarize(
    cumUnder10 = sum(TotalPct, na.rm = T),
    cumUnder10M = sum(MalePct, na.rm = T),
    cumUnder10F = sum(FemalePct, na.rm = T))


print(result_age_3)


```

#### The Overall Under 10 Population Percentage by District.

```{r}
district_under10 <- bind_rows(result_age, result_age_2, result_age_3)

```


#### The three different datasets are ready  :Overall Population, Population Under 10 years of age, Usually employed Population over 10 years.

```{r}
# three data.frames to be merged are emp_info, district_under10, popn_df
# let all have the same name for district_column
popn_df <- popn_df %>% rename(district_name = Group) 
popn_df <- popn_df  %>% arrange(district_name) %>% 
  mutate(district_id = 1:n())


district_under10 <- district_under10 %>% rename(district_name = District) 
district_under10 <- district_under10 %>% filter(!is.na(district_name) & !duplicated(district_name)) %>% 
  arrange(district_name) %>% 
  mutate(district_id = 1:n())

View(district_under10)

emp_info <- emp_info %>% 
  mutate(district_name = ifelse(district_name == "MOHOTTARI", "MAHOTTARI",district_name)) %>% 
  arrange(district_name) %>% 
  mutate(district_id = 1:n())

View(emp_info)


a <- right_join(popn_df, district_under10, by = c("district_id"))

b <- left_join(a, emp_info, by = c("district_id")) %>% select(-1, -7) %>% 
   mutate(
    district_name = case_when(
      district_name == "DHANKUTA" ~ "dhak",
      district_name == "SINDHUPALCHOK" ~ "sinp",
      district_name == "TERHATHUM" ~ "tehr",
      district_name == "DADELDHURA" ~ "dadh",
      district_name == "DOLKHA" ~ "DOLAKHA",
      district_name == "MOHOTTARI" ~ "MAHOTTARI",
      TRUE ~ district_name
    )
  ) %>% 
  mutate( district_abbrev = tolower(substr(district_name, 1, 4)))

View(b)
# b is now the working version

# Let's now merge this with the conflict data. 
c <- read_dta("Conflict Data/conflict_collapsed.dta")
final_conflict <- left_join(c, b, by = c("district_abbrev"))
View(final_conflict)

final_conflict <- final_conflict %>% 
  mutate(
    TotalPopn = as.numeric(TotalPopn),
    MalePopn = as.numeric(MalePopn),
    FemalePopn = as.numeric(FemalePopn)
  ) %>% 
  mutate(popn_over_10 = (1- cumUnder10/100) * TotalPopn)


final_conflict %>% 
  group_by(treatment) %>% 
  summarize(mean(total_emp/popn_over_10))

write_dta(final_conflict, "final_conflict.dta")
```

