---
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r}
setwd("/home/suhishan/Documents/Final Sem Research/Conflict/R files/")
library(haven)
library(tidyverse)
library(stargazer)
library(patchwork)
library(dagitty)
library(sf)
library(ddecompose)
library(DRDID)
library(xtable)
library(purrr)

theme_set(theme_minimal() +
            theme(panel.grid = element_blank()))

```


#Load Datasets.

```{r}
nlfs <- read_dta("appended_nlfs.dta") # Only people aged 10 and above. 
nlfs <- nlfs %>% 
  mutate(post = ifelse(nlfs_year == 2008, 1, 0))
c <- read_dta("final_conflict.dta")

# Renaming and mutating most of the variables that I will need.


#select only the relevant variables. 
c <- c %>% select(
  distname, elevation_max,norm_forest, pov_rate, district_abbrev, 
  best_est, 30:51, incidents
)

c <- c %>% mutate(
    forest_cover = round(norm_forest*100, 2),
    poverty_rate = round(pov_rate* 100, 2), #note: Dolpa, Mustang and          Rasuwa don't have poverty rate estimates.
    # Manang and Muustang (NA no conflict deaths) turned to 0 
    conflict_deaths = ifelse(is.na(best_est),
                             0,
                             best_est)
    )
```


Let's use Forest Cover as treatment and control i.e. if a district's forest cover is greater than the 75th percentile, it goes into treatment and otherwise it goes into control. 


```{r}
c <- c %>% mutate(
  treatment_f = ifelse(forest_cover  > quantile(forest_cover, 0.75),
                       1, 0),
  treatment_crude = 
    ifelse(conflict_deaths > quantile(conflict_deaths, 0.75), 
                           1, 0)
)

# Merge with the nlfs data.
c_merged <- left_join(nlfs, c, by = c("district_abbrev"))

c_merged <- c_merged <- c_merged %>% mutate(
  id = as.numeric(1:n()),
  post = as.double(ifelse(nlfs_year == 2008, 1, 0))
)

```

Now calculating the normalized difference of some observable characteristics that may have impacted untreated potential outcomes trend. 

```{r}
#function to calculate normalized difference
norm_difference <- function(t, x) {
  mean_t <-  mean(x[t == 1], na.rm = T)
  mean_c <-  mean(x[t == 0], na.rm = T)
  sd_t <-  sd(x[t == 1],na.rm =T)
  sd_c <- sd(x[t==0],na.rm = T )
  norm_diff = (mean_t - mean_c) / sqrt(0.5 * (sd_t^2 * sd_c^2))
  return (round(norm_diff, digits = 4))
}

c_merged_98 <- c_merged %>% filter(nlfs_year == 1998)


table_norm <- c_merged_98 %>% 
  select(age, years_of_edu_all, years_of_edu, hindu,
         brahmin_chhetri, sex, marital_status,
         treatment_f, hhsize,
         ever_school) %>% 
  summarize(across(
    .cols = -treatment_f,
    .fns = list(
      norm_diff = ~norm_difference(treatment_f, .x),
      mean_t  = ~ mean(.x[treatment_f == 1], na.rm = T),
      mean_c = ~mean(.x[treatment_f == 0], na.rm = T)),
    .names = "{fn}_{.col}"
  )) %>% 
 pivot_longer(
    cols = everything(),
    names_to = "stat_var", values_to = "value"
  ) %>% 
  extract(stat_var, into = c("stat", "variable"),
          regex = "(norm_diff|mean_t|mean_c)_(.+)") %>% 
  pivot_wider(
    names_from = stat, values_from = value
  )
table_norm
print(xtable(table_norm), file = "../First Draft/forest_table_norm.tex",
      include.rownames = F)

```


Now for the covariate differences:

```{r}
d1 <- c_merged %>% 
  select(age, years_of_edu_all, years_of_edu, hindu,
         brahmin_chhetri, sex, marital_status,
         treatment_f, hhsize,post,
         ever_school) %>% 
  group_by(treatment_f) %>% 
  summarize(
    across(
      .cols = -post,
      .fns = list(
        delta = ~ mean(.x[post == 1], na.rm = T) - mean(.x[post == 0], 
                                                        na.rm = T)),
      .names = "{.col}_{.fn}"
    ),
    .groups = "drop") %>% 
    pivot_longer(cols = -treatment_f, names_to = "variables",
                 values_to = "delta") %>% 
  pivot_wider(names_from = treatment_f, values_from = delta,
              names_prefix = "delta_")


```

Now for normalized differences:

```{r}
#This function is to calculate normalized difference in delta_X, so calculate mean difference in post/pre for both treatment and control, and also calculate the sd of the differences. 

norm_diff_delta <- function(t, post, x) {
  mean_delta_c = mean(x[t==0 & post ==1 ], na.rm =T) 
                  - mean(x[t == 0 & post == 0], na.rm = T)
  mean_delta_t = mean(x[t==1 & post ==1 ], na.rm = T) 
                  - mean(x[t == 1 & post == 0], na.rm = T)
  
  sd_delta_c = sd(x[t==0 & post ==1 ], na.rm = T) 
                  - sd(x[t == 0 & post == 0], na.rm = T)
  sd_delta_t = sd(x[t==1 & post ==1 ], na.rm = T) 
                  - sd(x[t == 1 & post == 0], na.rm = T)
  
  norm_diff = (mean_delta_t - mean_delta_c)/
    sqrt(0.5 * (sd_delta_t^2 * sd_delta_c^2))
  
  return (round(norm_diff, 4))
}

d2 <- c_merged %>% 
  select(age, years_of_edu_all, years_of_edu, hindu,
         brahmin_chhetri, sex, marital_status,
         treatment_f, hhsize,post,
         ever_school) %>% 
  summarize(
    across(
      .cols = -c(treatment_f, post),
      .fns = list(
        norm_diff_delta = ~ norm_diff_delta(treatment_f, post, .x)
      ),
      .names = "{.col}"
    )
  ) %>% pivot_longer(everything())

table_norm_delta <- bind_cols(d2, d1) %>% 
  select(-variables) %>% 
  rename(`2008 - 1998 Covariate Differences` = name, 
         `Norm Diff` = value,
         Control = delta_0,
         Treatment = delta_1)
print(xtable(table_norm_delta), 
      file = "../First Draft/forest_table_norm_delta.tex",
      include.rownames = F)

```

Let's graph the propensity scores a

# Propensity Score Model. (for Transparency)

Here, we use the pre-period 1998 data to construct a logit model where treatment status is regressed on covariates that may have influenced treatment assignment i.e. Regress treatment status on age, years of education, brahmin_chhetri and hindu for 2020.


```{r}
c_merged_98 <- c_merged_98 %>% filter(!is.na(years_of_edu_all) & !is.na(poverty_rate))

ps <- glm(treatment_f ~ age + ever_school + hindu + brahmin_chhetri + poverty_rate + hhsize, data = c_merged_98, family = binomial(link = "logit") )
summary(ps)


c_merged_98$pscore <- predict(ps, type = "response")

c_merged_98 %>% 
  ggplot(aes(x = pscore, fill = factor(treatment_f)))+
  geom_density(alpha = 0.5)

```


Let's do the drDiD

```{r}
ipwdid(yname = "usually_emp", tname = "post", idname = "id",
      dname = "treatment_crude",
      data = c_merged, panel = FALSE, boot = F, nboot = 199)


# Which districts overlap and which don't


c_merged %>% group_by(post,treatment_crude) %>% 
  summarize(mean(usually_emp, na.rm = T))





```

Let's try and do every possible treatment group assignment and seet the distribution of values. 

So, I've got two different signs for my difference in difference values, when ideally it should've been at least the same sign. I want to now randomize the treatment among districts and see the values of many difference DiDs that arise from it. 

```{r}
#Let's first see how to calculate simple DiD.

c_merged %>% 
  group_by(nlfs_year) %>% 
  summarize(diff = mean(usually_emp[treatment_f == 1]) - 
              mean(usually_emp[treatment_f == 0])) %>% 
  summarize(.[2,2] - .[1,2]) %>% 
  pull()
  
#Let's make a function of this.

simple_did <- function(d){
  did_estimate <- d %>% 
    group_by(post) %>% 
    summarize(diff = mean(usually_emp[t == 1]) - 
                mean(usually_emp[t == 0])) %>% 
    summarize(.[2,2] - .[1,2]) %>% 
    pull()
  
  return(round(did_estimate, 5))
}


```


Let's now try to compute:

```{r}
n_sim <- 1e4 # no. of simulations

district_abbrev <- unique(c$district_abbrev)

# A list of n_sim district and treatment assignment. 
assignments <- map(1:n_sim, ~{
  tibble(district_abbrev = district_abbrev,
         t = rbinom(length(district_abbrev), 1, 0.3))
})


compute_did <- function(treatment_assignment) {
  d <- nlfs %>% 
    left_join(treatment_assignment,
              by = c("district_abbrev"))
  return (simple_did(d))
}

did_estimates <- map_dbl(assignments, compute_did)


```

Plotting
```{r}
hist <- tibble(did_estimates = did_estimates) %>% 
ggplot(aes(x = did_estimates))+
  geom_histogram(color = "black", fill = "skyblue",
                 bins = 30)+
  geom_vline(xintercept = c(-0.052, 0.026), linetype = 2,
             color = c("red", "black"))+
  labs(x = "Simple DiD Estimate",
       title = "A histogram of 10000 simulated treatment assignments",
       subtitle = "Treatment assignment binomially with p = 0.3")

density <- tibble(did_estimates = did_estimates) %>% 
  ggplot(aes(x = did_estimates))+
  geom_density(alpha = 5/10, fill = "skyblue")+
  geom_vline(xintercept = c(-0.052, 0.026), linetype = 2,
             color = c("red", "black"))+
   annotate("text", label = "Crude Estimate", x = 0.05 , y = 10)+
    annotate("text", label = "Forest Cover \n as treatment", x = -0.07 , y = 10)+
  labs(x = "Simple DiD Estimate",
       title = "Density plot  of 10000 simulated treatment assignments",
       subtitle = "Treatment assignment binomially with p = 0.3")

ggsave("simulation_histogram.jpg", plot = hist, height = 20, width = 30, units = "cm",  bg = "white", path = "../First Draft")

ggsave("simulation_density.jpg", plot = density, height = 15, width = 30, units = "cm",  bg = "white", path = "../First Draft")


```


